Probabilistic Catalogs for Crowded Stellar Fields

### 2013-01-31 paper/response.md

Itemized Responses
==================

"Abstract seems to be overselling the case in multiple instances; for example, "introduce" may be too strong given Stetson's work on DAOPHOT"

- We have changed "introduce" to "present". Related approaches definitely exist.

"SExtractor "significantly underestimates" and "incorrect inferences"? What do "significant" and "incorrect" mean here - something of practical importance that astronomers should be scared of? The results presented in the paper didn't convince me."

- We were referring to the fact that SExtractor couldn't find all the stars.
This would be of practical importance in some instances but not others, it depends on whether finding all the stars or quantifying the faint stars is important.
The abstract has (**NOT YET**) been clarified to be more specific and realistic about the differences between the methods.

"The analysis of test cases is very superficial and the reader is left wondering about the actual performance. For example, what is the difference in photometric ans astrometric precision between the new method and SExtractor on an *object-by-object* basis? Surely at the bright end objects must be identical! What is completeness and contamination as a function of brightness? I return to this point below - something *must be wrong* with Fig. 6 and corresponding discussion. The bottom line is that currently Sections 5 and 6 are insufficient to assess the performance of this method, both in absolute sense and relative to SExtractor's performance. The unbelievable claims about SExtractor are not substantiated."

- The idea of comparing precision on an object-by-object basis is a very good one. (**I'm working on it**).

### 2013-02-24 paper/ms.tex
Anna

\section{Acknowledgements}
It is a pleasure to thank
  Jonathan Goodman (NYU),
  Fengji Hou (NYU),
  Dustin Lang (CMU),
  Geraint Lewis (Sydney), and
  Phil Marshall (Oxford)
for their comments and discussions.
The referee is thanked for their thoughtful comments which helped us to improve
the paper.
BJB would like to thank Tommaso Treu (UCSB) for his support, and
Wayne Stewart and Arden Miller (Auckland) for their encouragement and advice.
DFM and DWH were partially supported by
   the US National Science Foundation (grant IIS-1124794) and
   the US National Aeronautics and Space Administration (grant NNX12AI50G).

>>>>

\section{Acknowledgements}
It is a pleasure to thank
  Anna Nierenberg (UCSB),
  Jonathan Goodman (NYU),
  Fengji Hou (NYU),
  Dustin Lang (CMU),
  Geraint Lewis (Sydney), and
  Phil Marshall (Oxford)
for their comments and discussions.
The referee is thanked for their thoughtful comments which helped us to improve
the paper.
BJB would like to thank Tommaso Treu (UCSB) for his support, and
Wayne Stewart and Arden Miller (Auckland) for their encouragement and advice.
DFM and DWH were partially supported by
   the US National Science Foundation (grant IIS-1124794) and
   the US National Aeronautics and Space Administration (grant NNX12AI50G).
